---
title: Activity 2-3 - Tidy Data
author: Purple
date: 09/10/2019
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
```

### Load and collect data

```{r load-data}
fship <- read_csv("data/The_Fellowship_Of_The_Ring.csv")
ttow <- read_csv("data/The_Two_Towers.csv")
rking <- read_csv("data/The_Return_Of_The_King.csv")
```

```{r collect-data}
lotr_untidy <- bind_rows(fship, ttow, rking)
str(lotr_untidy)
lotr_untidy
```

### Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget 
to label your code chunk. Do not use spaces in code chunk labels.)

### Exercise 4

...

### Exercise 5

...

### Exercise 6

...

### Exercise 7

...
