---
title: Activity 2-3 - Tidy Data
author: Purple
date: 09/10/2019
output: 
  html_document: 
    keep_md: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
```

### Load and collect data

```{r load-data}
fship <- read_csv("data/The_Fellowship_Of_The_Ring.csv")
ttow <- read_csv("data/The_Two_Towers.csv")
rking <- read_csv("data/The_Return_Of_The_King.csv")
fship
```

```{r collect-data}
lotr_untidy <- bind_rows(fship, ttow, rking)
str(lotr_untidy)
lotr_untidy
```

### Exercise 1

This data is untidy because there were multiple observations in one row.

### Exercise 2
```{r}
lotr_tidy <- lotr_untidy %>% 
  gather(key = 'Gender', value = 'Words', Female, Male)
lotr_tidy

write_csv(lotr_tidy, path = "data/lotr_tidy.csv")
```

```{r}
f <- read_csv("data/Female.csv")
m <- read_csv("data/Male.csv")
lotr_tidy <- bind_rows(f, m)

write_csv(lotr_tidy, path = "data/lotr_tidy.csv")
```

### Exercise 3

``` {r three}
lotr_tidy %>%
  group_by(Race) %>%
  summarise(total = sum(Words))
```

### Exercise 4

``` {r four}
lotr_tidy %>%
  group_by(Film) %>%
  summarise(total = sum(Words))
```

### Exercise 5

```{r learning-the-spread-function}
lotr_tidy%>%
  group_by(Film,Gender)%>%
  summarise(total=sum(Words))
lotr_tidy%>%
  group_by(Film,Gender)%>%
  summarise(total=sum(Words)) %>%
  spread(Gender,total)
```
The spread data is easier to view, because it reduces the amount of rows the reader has to peruse without creating more columns by condensing the total words spoken with the Gender for each observation (in this case, each film of lotr). 


### Exercise 6

```{r Combined-Gender-Race-Words-Spoken}
lotr_tidy%>%
  unite("Race_Gender", Race:Gender)%>%
  group_by(Film,Race_Gender)%>%
  summarise(total=sum(Words)) %>%
  spread(Race_Gender,total)
```

### Exercise 7

```{r creating-three-ori-tables}
lotr_tidy%>%
  group_by(Film,Race,Gender)%>%
  summarise(total=sum(Words)) %>%
  spread(Gender,total)%>%
  ungroup()%>%
  group_split(Film)
```


